---
title: "Initial Korean covid 19"
author: "Milton Rodas"
date: "Fall Semester"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?






## Graphical results - use ggplot commands to do this  



  




```{r}
barchartGC(~result + sex,data=kRdata)
barchartGC(~result + Sex,data=kRdata, type="percent")

```

The majority of people who where alive were female, at anout 55% while the rest were males, about 45%. However out of the population that died, nearly 65% were males while 45% were females. This means there was a significant difference between the amount of make that died and the amount of females that died, males being the majority as they nearly doubled the amount of deaths on females.
  
## Numerical results


## Inferential results 




## Conclusions

